% LaTeX file for resume
% This file uses the resume document class (res.cls)

\documentclass[margin]{res}
\usepackage [brazil]{babel}      % nomes e hifenaçã em português

\usepackage{t1enc}               % Permite digitar os acentos de forma normal
\usepackage[utf8]{inputenc}

\topmargin=-0.5in                % start text higher on the page
\setlength{\textheight}{10in}    % increase text height to fit resume on 1 page

\begin{document}

\name{\textit{Diogo Justen}}
\address{São José, BR \\ diogojusten@gmail.com \\ Phone: +55 (48) 9994-4758 }

\begin{resume}

\section{Summary}
I'm a Computer Engineer since 2012, but I started programming long time before that. I’m passionate about understanding how things work and what fascinates me most is
the world of computing. I consider myself autodidact because I like to learn new technologies all the time and I can do it very quickly. At college C was the first language I learnt, also other programming languages, such as Assembly x86, Java, Shell Script, Python, VHDL and Matlab and protocols as Zigbee and MiWi.

I've been working for long time as developer and everytime involving Embedded System with Linux, as a result I acquired a lot knowledge in this field. In the last year I focused to work mainly with device drivers in kernel space. 

I worked in companies with several different technologies and it made me an open minded developer, with can-do attitude and a good interpersonal relationship. I love embedded system, specify kernel space, when is necessary to do a interface between hardware and software. Currently I’m working with Embbeded System, developing a new generation of Digital Fault Recorder in south Brazil, but looking for new challenges around the world.

\section{Education}
 IFSC, Post-graduation Specializing Development of Electronic Products, expected finish in December 2016.\\
 UNIVALI University, BSc in Computer Engineering, June 2012.

\section{Experience}
\vspace{-0.1in}
    \begin{tabbing}
    \hspace{2.3in}\= \hspace{1.7in}\= \kill % set up two tab positions
    \textbf{GE Grid Solution}    \>\>\textbf{May 2013 - Present}\\
    \textit{Development Analyst}\\
    \textbf{Main Technologies}: C, Shell Script, Python, Embedded Linux, Device Drivers,\\
                                Multithreading, DMA, System on Chip and FPGA;
    \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
    \vspace{2mm}
Development embedded software for critical applications for electrical systems. We're using buildroot to build a custom embedded Linux, we also use C, Python, device drivers, ShellScript, sockets, multithreading, static code analyzer, Test Driven Development (TDD), U-Boot, Sockets, Modbus, DNP3, NTP, IEC61850 standard, Sampled Values, XML, x86, ARM, SVN, Git, GDB, DMA, interrupts.

We work with full software lifecycle: specification, design, implementation, integration, debug and maintenance. Also development software using Kanban.

Projects that participated: Digital Fault Recorder with PMU and TWFL (Models RPV 310 and RPV 311, these use x86) and a new generation of Digital Fault Recorder than use ARM.

\vspace{-0.1in}
    \begin{tabbing}
    \hspace{2.3in}\= \hspace{1.7in}\= \kill
    \textbf{Digitro Tecnologia}    \>\>\textbf{Oct 2008 - May 2013}\\
    \textit{Backend Developer}\\
    \textbf{Main Technologies}: C, ShellScript, Linux uClinux and Monteray, Blackfin, VoIP,\\ protocol UDP, TCP, TLS, SIP, RTP;
    \end{tabbing}\vspace{-20pt}
    \vspace{2mm}
In this company was my first job as a software developer. Firstly I fixed bugs in a project of IP Phone and have been improved a scripts to automate the recording Firmware in the factory. After I also worked in other products(ATA and Smartcell). Two year later I started to work in a new project to develop a new generation of IP Phone with touch screen, color display, using Blackfin processor with uCLinux distribution. We used U-Boot, GLib, GObject, GDBus, Sofia-SIP as SIP stack, C, ShellScript and jhbuild.

We used Scrum methodology and SVN software versioning.

Projects that participated: IP Phone Mono, IP Phone, color with touch-screen, SmartCell and ATA. 

\section{Skills Base} \textit{Programming Languages}: C, ShelScript, Python and a little of VHDL and Java;

	\textit{Agile practices}: TDD, SCRUM, Kanban, Pair programming, Clean code, Code Review;
	
	\textit{Tools}: Git, Svn, Makefile, Jenkins, CPPCheck;
	
	\textit{Languages}: Fluent in Portuguese, Intermediate in English and Beginner in German;

	\textit{Platforms}: Linux and Windows;
	
\section{More Info} \textit{Linkedin}: https://www.linkedin.com/in/diogo-justen-31252054

\end{resume}
\end{document}
